Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility

### 2025-12-03 paper/02-antecedents.qmd
Up draft presentation

Social mobility and meritocratic perceptions are closely intertwined in the acculturation mechanism, although the direction of this link can vary across trajectories and contexts. A large body of work consistently shows that upwardly mobile individuals tend to interpret their trajectory through a meritocratic lens, reading their success as evidence that effort and ability are rewarded and reinforcing individualistic attributions of poverty and wealth [@bucca_merit_2016; @gugushvili_intergenerational_2016; @shariff_income_2016; @mijs_belief_2022], even in a highly unequal and low mobility setting were the narratives of individual success reinforces [@deng_its_2025]. Studies of economic elites in Chile similarly report strong endorsement of meritocracy, with respondents attributing their ascent mainly to talent and business or leadership skills [@atria_economic_2020]. Evidence on downward or blocked mobility is more ambivalent. Exposure to low-mobility contexts and experiences of downward mobility are associated with weaker beliefs that effort is rewarded, lower just-world and opportunity beliefs, and stronger structural attributions for success and failure [@gugushvili_intergenerational_2016; @davidai_why_2018; @day_movin_2017; @mijs_how_2022]. Yet, under strong meritocratic convictions, status loss can also be internalised as personal failure, sustaining system-justifying attitudes and the legitimation of existing hierarchies as a psychological defence strategy [@day_movin_2017; @mau_inequality_2015; @deng_its_2025].  In sum, upward mobility is generally associated with stronger meritocratic perceptions, whereas downward mobility is more closely linked to structural explanations of inequality, without necessarily eroding meritocratic convictions.

The ways in which social mobility trajectories shape interpretations of meritocracy can determine whether mobility translates into stronger or weaker support for market-based pension welfare. Following Mau’s [-@mau_inequality_2015] account of the “majority class”, upward mobility is expected to strengthen market-based welfare not only because material interests change, but because those who rise come to read their story as one of individual effort and talent rewarded. In this view, markets are seen as fair arenas that properly allocate pensions and other welfare benefits according to merit, so upwardly mobile individuals with strong meritocratic convictions should be especially prone to endorse commodified pensions. In contrast, downward mobility typically fosters de-commodifying demands, yet under strong meritocratic perceptions, status loss may be read as individually deserved, weakening—or even reversing—its usual de-commodifying pattern, as market outcomes are still viewed as broadly fair regardless of direction. Empirical research on redistribution and attitudes toward inequality supports this mechanism. Survey studies suggest that subjective social mobility shapes support for redistribution and pension spending through self-serving bias [@schmidt_experience_2011; @gugushvili_subjective_2017], although recent work indicates that this mechanism is evident only under explicit constraints in experimental designs [@molina_its_2019]. More in line with the acculturation theories, experimental reserach has shown that exposure to upward-mobility information or self-made narratives reduces support for redistribution, increases tolerance of inequality and system justification, and even legitimises exploitative work conditions, whereas exposure to low or downward mobility produces the opposite pattern; crucially, these effects are partly mediated by stronger meritocratic perceptions [@matamoros-lima_social_2025; @shariff_income_2016; @deng_its_2025]. In this framework, meritocratic perceptions condition the attitudinal consequences of mobility by amplifying the pro-market effects of upward mobility and muting the critical potential of downward mobility; thus, I treat meritocratic perceptions as a moderating mechanism linking intergenerational mobility to preferences for pension commodification.

>>>>

Social mobility and meritocratic perceptions are closely intertwined in the acculturation mechanism, although the direction of this link can vary across trajectories and contexts. A large body of work consistently shows that upwardly mobile individuals tend to interpret their trajectory through a meritocratic lens, reading their success as evidence that effort and ability are rewarded and reinforcing individualistic attributions of poverty and wealth [@bucca_merit_2016; @gugushvili_intergenerational_2016; @traini_climbing_2025; @mijs_belief_2022], even in a highly unequal and low mobility setting were the narratives of individual success reinforces [@deng_its_2025]. Studies of economic elites in Chile similarly report strong endorsement of meritocracy, with respondents attributing their ascent mainly to talent and business or leadership skills [@atria_economic_2020]. Evidence on downward or blocked mobility is more ambivalent. Exposure to low-mobility contexts and experiences of downward mobility are associated with weaker beliefs that effort is rewarded, lower just-world and opportunity beliefs, and stronger structural attributions for success and failure [@gugushvili_intergenerational_2016; @davidai_why_2018; @day_movin_2017; @mijs_how_2022]. Yet, under strong meritocratic convictions, status loss can also be internalised as personal failure, sustaining system-justifying attitudes and the legitimation of existing hierarchies as a psychological defence strategy [@day_movin_2017; @mau_inequality_2015; @traini_climbing_2025].  In sum, upward mobility is generally associated with stronger meritocratic perceptions, whereas downward mobility is more closely linked to structural explanations of inequality, without necessarily eroding meritocratic convictions.

The ways in which social mobility trajectories shape interpretations of meritocracy can determine whether mobility translates into stronger or weaker support for market-based pension welfare. Following Mau’s [-@mau_inequality_2015] account of the “majority class”, upward mobility is expected to strengthen market-based welfare not only because material interests change, but because those who rise come to read their story as one of individual effort and talent rewarded. In this view, markets are seen as fair arenas that properly allocate pensions and other welfare benefits according to merit, so upwardly mobile individuals with strong meritocratic convictions should be especially prone to endorse commodified pensions. In contrast, downward mobility typically fosters de-commodifying demands, yet under strong meritocratic perceptions, status loss may be read as individually deserved, weakening—or even reversing—its usual de-commodifying pattern, as market outcomes are still viewed as broadly fair regardless of direction. Empirical research on redistribution and attitudes toward inequality supports this mechanism. Survey studies suggest that subjective social mobility shapes support for redistribution and pension spending through self-serving bias [@schmidt_experience_2011; @gugushvili_subjective_2017; @traini_climbing_2025], although recent work indicates that this mechanism is evident only under explicit constraints in experimental designs [@molina_its_2019]. More in line with the acculturation theories, experimental reserach has shown that exposure to upward-mobility information or self-made narratives reduces support for redistribution, increases tolerance of inequality and system justification, and even legitimises exploitative work conditions, whereas exposure to low or downward mobility produces the opposite pattern; crucially, these effects are partly mediated by stronger meritocratic perceptions [@matamoros-lima_social_2025; @shariff_income_2016; @deng_its_2025]. However, recent research has tested Piketty's (1995) hypothesis that meritocracy would mediate the effect of upward social mobility on redistributive preferences, without finding support for it [@rodriguez_intergenerational_2024]. In this framework, meritocratic perceptions condition the attitudinal consequences of mobility by amplifying the pro-market effects of upward mobility and muting the critical potential of downward mobility; thus, I treat meritocratic perceptions as a moderating mechanism linking intergenerational mobility to preferences for pension commodification.

### 2025-12-03 paper/05-discussion.qmd
Up draft presentation

The findings reveal a tension in Chileans’ judgements of market-based pension welfare. Across 2016, 2018 and 2023, large majorities reject the claim that it is fair for higher-income people to obtain better pensions than those with lower incomes. However, a non-trivial—and growing—minority endorses this principle, with the sharpest increase between 2018 and 2023. Market-based pension allocation thus remains a minority view. However, it is becoming more common, in line with longitudinal evidence of rising support for income-based access to welfare services in Chile [@castillo_perceptions_2025]. This coexistence unfolds in a system of mandatory, privately managed, defined-contribution accounts that tightly link old-age income to earnings, contribution density and financial returns. This design has produced low and unequal pensions and state interventions against old-age poverty [@madero-cabib_private_2019; @galvez_pensiones_2024], while framing pensions as personal investments rather than solidarity-based rights and promoting individual responsibility and contribution-based desert [@borzutzky_pension_2012]. The Chilean case fits evidence that supports the claim that income-based welfare access is stronger in liberal, marketised regimes [@lindh_public_2015]. This coexistence also echoes recent pension conflict—from the “No+AFP” protests to post-pandemic withdrawals and the “Con mi plata NO” mobilisation [@galvez_con_2023]—and illustrates mixed policy feedback: the same regime generates rights-based critiques and proprietarian defences of pension commodification. Together, these patterns show that, despite discontent and a legitimacy crisis, support for pension commodification remains salient, raising the question of which social trajectories and beliefs underpin it.

@@

The second set of hypotheses examined whether meritocratic perceptions condition the effects of intergenerational mobility. Building on acculturation accounts and self-serving bias arguments [@jaime-castillo_social_2019; @gugushvili_subjective_2017], I expected mobility to affect preferences for pension commodification not only through material self-interest but also through shifts in normative frames of distributive justice. Prior research shows that upwardly mobile individuals tend to interpret their trajectory through a meritocratic lens, reading their success as evidence that effort and ability are rewarded and reinforcing individualistic attributions of poverty and wealth. In contrast, downward or blocked mobility is more often associated with structural explanations of inequality and more ambivalent meritocratic beliefs, sometimes including the internalisation of status loss as personal failure [@atria_economic_2020; @bucca_merit_2016; @gugushvili_intergenerational_2016; @davidai_why_2018; @day_movin_2017; @mijs_how_2022; @deng_its_2025]. Following Mau’s [-@mau_inequality_2015] account of the “majority class”, I therefore expected upward mobility under strong meritocratic convictions to be especially conducive to endorsing commodified pensions, and strong meritocracy to dampen the usual de-commodifying effect of downward mobility. Empirically, however, the interaction models offer little support for this mechanism. Meritocratic perceptions do not systematically moderate the mobility effects identified in the primary analysis, and the few trajectory-specific patterns that tentatively point in the expected direction are small and imprecisely estimated. This result contrasts with survey and experimental studies showing that upward mobility experiences or exposure to self-made narratives reduce support for redistribution and public pension spending partly by reinforcing meritocratic convictions [@schmidt_experience_2011; @gugushvili_subjective_2017; @molina_its_2019; @shariff_income_2016; @matamoros-lima_social_2025; @deng_its_2025]. One possibility is that, in this context, intergenerational occupational mobility—as operationalised here—has limited impact on meritocratic perceptions, which appear more weakly tied to mobility trajectories than previous research suggests and more strongly anchored in broader socialisation processes and class-specific cultures.

This study makes several contributions. Substantively, it offers one of the first systematic analyses of preferences for pension commodification in Chile’s highly unequal and marketised pension regime, addressing Mau’s [-@mau_inequality_2015] question of why core elements of neoliberal welfare arrangements gain public acceptance. By showing that upward and downward intergenerational mobility into and out of upper-class positions causally shape support for market-based pension allocation, the findings highlight social mobility as a key source of legitimation for commodified pensions. Second, the article advances research on market justice and market-based welfare preferences by moving beyond static class locations and showing how intergenerational occupational mobility structures support for pension commodification in ways that partly echo, but also refine, existing evidence on class, income and financial returns. Third, the null results for the moderating role of meritocratic perceptions nuance accounts that tightly link mobility, meritocracy and the embrace of neoliberal welfare: in this context, mobility effects on pension commodification preferences appear to operate independently of meritocratic beliefs. Finally, the study contributes methodologically by applying Breen and Ermisch’s [-@breen_effects_2024] causal framework of mobility effects to survey data, formalising mobility as origin-specific treatment effects and estimating these using linear probability models with inverse probability weighting.

Despite these contributions, the study has limitations that should be acknowledged and read as avenues for future improvement. First, the causal estimates hinge on the construction of inverse probability weighting within Breen and Ermisch’s [-@breen_effects_2024] framework. Identification relies on conditional independence given a relatively limited set of origin-side covariates, together with positivity and SUTVA. Entropy balancing helps to enforce covariate balance and mitigate selection on observables, but unmeasured confounding cannot be ruled out. Sensitivity analyses suggest moderate robustness to omitted variables; therefore, the estimates should be interpreted with caution. Second, while the analysis identifies mobility effects on preferences, it does not explain why or how they arise. The results are analysed through material self-interest and acculturation mechanisms. Still, the study does not implement formal causal mediation analysis, nor can it determine whether meritocratic perceptions function as mediators rather than mere correlates. Third, the findings are context-specific: they are derived from Chile, a highly unequal and strongly marketised pension regime, which enhances internal validity but limits external validity. The patterns documented here, therefore, cannot be straightforwardly generalised to countries with different welfare institutions, mobility regimes or levels of inequality, and should be seen as a theoretically informed case study rather than a cross-national pattern.

Future research could extend these findings in several directions. First, there is a need for richer measures of preferences for pension commodification. This study relies on a single item that conflates income-based allocation and fairness judgments; better items that separate justice principles and dimensions of commodification would allow a finer assessment of how people evaluate pensions as income-conditioned commodities. Second, methodological limitations could be addressed by including more detailed origin-side covariates and life-course data, repeated measures of meritocratic perceptions, and causal mediation analyses that unpack mechanisms such as material self-interest, risk exposure, and meritocratic frames, alongside alternative measures of mobility based on class schemas, income trajectories, or wealth. Third, comparative designs would clarify how institutional context shapes the attitudinal consequences of intergenerational mobility. Applying similar causal strategies in countries with different welfare regimes, levels of inequality, mobility patterns, and degrees of pension marketisation would show whether the Chilean pattern is context-specific or part of a broader configuration linking mobility, merit and support for market-based welfare. Ultimately, clarifying when and for whom market allocation of pensions is judged fair is crucial to understanding the legitimate reach of welfare commodification in unequal, marketised societies.

>>>>

The findings reveal a tension in Chileans’ judgements of market-based pension welfare. Across 2016, 2018 and 2023, large majorities reject the claim that it is fair for higher-income people to obtain better pensions than those with lower incomes. However, a non-trivial—and growing—minority endorses this principle, with the sharpest increase between 2018 and 2023. Market-based pension allocation thus remains a minority view. However, it is becoming more common, in line with longitudinal evidence of rising support for income-based access to welfare services in Chile [@castillo_perceptions_2025]. This coexistence unfolds within a system of mandatory, privately managed, defined-contribution accounts that tightly link old-age income to earnings, contribution density and financial returns [@madero-cabib_private_2019; @galvez_pensiones_2024], and that frame pensions as personal investments rather than solidarity-based rights, promoting individual responsibility, self-economisation, contribution-based desert and casting workers as employee-entrepreneurs who must navigate financial risks and “make their money work” [@borzutzky_pension_2012]. The Chilean case thus fits evidence that income-based welfare access is more strongly endorsed in liberal, marketised regimes [@lindh_public_2015].This coexistence also echoes recent pension conflict—from the “No+AFP” protests to post-pandemic withdrawals and the “Con mi plata NO” mobilisation [@galvez_con_2023]—and illustrates mixed policy feedback: the same regime generates rights-based critiques and proprietarian defences of pension commodification. Together, these patterns suggest that, despite discontent and a legitimacy crisis, support for pension commodification remains a salient and contested orientation, raising the question of which social trajectories and beliefs underpin it.

@@

The second set of hypotheses examined whether meritocratic perceptions condition the effects of intergenerational mobility. Building on acculturation accounts and self-serving bias arguments [@jaime-castillo_social_2019; @gugushvili_subjective_2017], I expected mobility to affect preferences for pension commodification not only through material self-interest but also through shifts in normative frames of distributive justice. Prior research shows that upwardly mobile individuals tend to interpret their trajectory through a meritocratic lens, reading their success as evidence that effort and ability are rewarded and reinforcing individualistic attributions of poverty and wealth. In contrast, downward or blocked mobility is more often associated with structural explanations of inequality and more ambivalent meritocratic beliefs, sometimes including the internalisation of status loss as personal failure [@traini_climbing_2025; @gugushvili_intergenerational_2016; @davidai_why_2018; @day_movin_2017; @mijs_how_2022; @deng_its_2025]. Following Mau’s [-@mau_inequality_2015] account of the “majority class”, I therefore expected upward mobility under strong meritocratic convictions to be especially conducive to endorsing commodified pensions, and strong meritocracy to dampen the usual de-commodifying effect of downward mobility. Empirically, however, the interaction models offer little support for this mechanism. Meritocratic perceptions do not systematically moderate the mobility effects identified in the primary analysis, and the few trajectory-specific patterns that tentatively point in the expected direction are small and imprecisely estimated. This result contrasts with survey and experimental studies showing that upward mobility experiences or exposure to self-made narratives reduce support for redistribution and public pension spending partly by reinforcing meritocratic convictions [@schmidt_experience_2011; @gugushvili_subjective_2017; @molina_its_2019; @shariff_income_2016; @matamoros-lima_social_2025; @deng_its_2025], and aligns with recent research that has shown that meritocracy does not mediate the effect of social mobility on redistributive preferences [@rodriguez_intergenerational_2024]. One possibility is that, in this context, intergenerational occupational mobility—as operationalised here—has limited impact on meritocratic perceptions, which appear more weakly tied to mobility trajectories than previous research suggests and more strongly anchored in broader socialisation processes and class-specific cultures.

The contributions of this study can be summarized as follows. Substantively, it offers one of the first systematic analyses of preferences for pension commodification in Chile’s highly unequal and marketised pension regime, addressing Mau’s [-@mau_inequality_2015] question of why core elements of neoliberal welfare arrangements gain public acceptance. By showing that upward and downward intergenerational mobility into and out of upper-class positions causally shape support for market-based pension allocation, the findings highlight social mobility as a key source of legitimation for commodified pensions. Second, the article advances research on market justice and market-based welfare preferences by moving beyond static class locations and showing how intergenerational occupational mobility structures support for pension commodification in ways that partly echo, but also refine, existing evidence on class, income and financial returns. Third, the null results for the moderating role of meritocratic perceptions nuance accounts that tightly link mobility, meritocracy and the embrace of neoliberal welfare: in this context, mobility effects on pension commodification preferences appear to operate independently of meritocratic beliefs. Finally, the study contributes methodologically by applying Breen and Ermisch’s [-@breen_effects_2024] causal framework of mobility effects to survey data, formalising mobility as origin-specific treatment effects and estimating these using linear probability models with inverse probability weighting.

Despite its merits, the study has limitations that should be acknowledged and read as avenues for future improvement. First, the causal estimates hinge on the construction of inverse probability weighting within Breen and Ermisch’s [-@breen_effects_2024] framework. Identification relies on conditional independence given a relatively limited but relevant set of origin-side covariates, together with positivity and SUTVA. Entropy balancing helps to enforce covariate balance and mitigate selection on observables, but unmeasured confounding cannot be ruled out. Sensitivity analyses suggest moderate robustness to omitted variables; therefore, the estimates should be interpreted with caution. Second, while the analysis identifies mobility effects on preferences, it does not explain why or how they arise. The results are analysed through material self-interest and acculturation mechanisms. Still, the study does not implement formal causal mediation analysis, nor can it determine whether meritocratic perceptions function as mediators rather than mere correlates. Third, the findings are context-specific: they are derived from Chile, a highly unequal country with a strongly marketised pension regime, which enhances internal validity but limits external validity. The patterns documented here, therefore, cannot be straightforwardly generalised to countries with different welfare institutions, mobility regimes or levels of inequality, and should be seen as a theoretically informed case study rather than a cross-national pattern.

Future research could extend these findings in several directions. First, there is a need for richer measures of preferences for pension commodification. This study relies on a single item that conflates income-based allocation and fairness judgments; better items that separate justice principles and dimensions of commodification would allow a finer assessment of how people evaluate pensions as income-conditioned commodities. Second, methodological limitations could be addressed by including more detailed origin-side covariates and life-course data, repeated measures of meritocratic perceptions, and causal mediation analyses that unpack mechanisms such as material self-interest, risk exposure, and meritocratic frames, alongside alternative mobility measures based on class schemas, income trajectories, or wealth. Third, comparative designs would clarify how institutional context shapes the attitudinal consequences of intergenerational mobility. Applying similar causal strategies in countries with different welfare regimes, levels of inequality, mobility patterns, and degrees of pension marketisation would show whether the Chilean pattern is context-specific or part of a broader configuration linking mobility, merit and support for market-based welfare [@mau_inequality_2015]. Ultimately, clarifying when and for whom market allocation of pensions is judged fair is crucial to understanding the legitimate reach of welfare commodification in unequal, marketised societies.

### 2025-12-03 paper/paper.qmd
Up borrador VF
Up draft presentation

---
title: "Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
    code-link: true
    title-block-banner: true
    theme:
      - pretty.scss
  pdf: 
    pdf-engine: xelatex
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/tesis-magister.bib"
csl: "../input/bib/apa6.csl"
author:
  - name: Andreas Laffert Tamayo
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 1
affiliations: 
  - id: 1
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
citeproc: true
abstract: | 
 My abstract
  \newline
 **Keywords**: Pension commodification · Intergenerational mobility · Causal inference · Meritocracy · Chile
link-citations: true
linestretch: 1.5
mainfont: Times New Roman
fontsize: 13pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

@@

This document was last modified at {{< modified >}}
and it was last rendered at {{< now >}}.

@@

{{< include 06-conclusion.qmd >}}

@@

{{< include 07-supplementary-material.qmd >}}

>>>>

---
title: "Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility"
date: today
date-format: "MMMM, YYYY"
format:
  html: 
    latex-environment: true
    code-fold: true
    html-math-method: katex
    number-sections: true
    code-link: true
    title-block-banner: true
    theme:
      - pretty.scss
  pdf: 
    pdf-engine: xelatex
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/tesis-magister.bib"
csl: "../input/bib/apa6.csl"
author:
  - name: 'Andreas Laffert Tamayo\thanks{This M.A. thesis in Sociology is one of my first achievements on the long path toward becoming an academic committed to the study of inequalities and to a public sociology. This journey would not have been possible without my relentless effort and the support of my family, friends and colleagues. Last but certainly not least, I want to acknowledge the motivation behind my research: the everyday processes through which neoliberalism is legitimised by ordinary people. This project was made possible through the financial support of ANID (BECAS/MAGÍSTER NACIONAL 2024) and the intellectual support and academic environment provided by the FONDECYT Regular project Nº 1250518. Any errors or omissions in this work are my sole responsibility. Comments are welcome at: andreas.laffert@uchile.cl}'
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 1
affiliations: 
  - id: 1
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
citeproc: true
abstract: | 
 The privatisation and marketisation of social services have been linked to feedback effects on public attitudes towards welfare and market inequality. From a moral-economy perspective, prior research shows that support for market-based access to core services depends on socio-structural position, inequality beliefs and institutional context. Yet, we know little about how citizens judge the fairness of pension commodification, and in particular how intergenerational mobility shapes these judgements and whether meritocratic perceptions condition this relationship. I address this gap by analysing preferences for market-based pension access in Chile, a highly unequal country with constrained mobility and a private pension system based on mandatory individual capitalisation that depends heavily on contribution histories. Drawing on three waves of the Chilean Longitudinal Social Survey (ELSOC; 3,435 observations on 1,787 individuals) and under explicit identification assumptions, I apply a recent causal framework for mobility effects that treats destination class as a treatment conditional on origin class, and estimate heterogeneous destination effects on support for pension commodification. Results show that upward mobility from middle to upper occupational status increases support for market-based pension access relative to immobility. In contrast, downward mobility from upper to middle or lower status reduces it. Meritocratic perceptions do not significantly moderate these effects, suggesting that mobility and meritocracy operate through largely separate pathways. These findings advance research on welfare marketisation by providing causal evidence on how intergenerational mobility shapes preferences for market-based welfare, and by assessing the potential moderating role of meritocratic perceptions in a highly commodified regime.
  \newline
 **Keywords**: Pension commodification · Intergenerational mobility · Causal inference · Meritocracy · Chile
link-citations: true
linestretch: 1.5
mainfont: Times New Roman
fontsize: 13pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

@@

@@

@@

{{< include 06-supplementary-material.qmd >}}
